\subsection{Endoplasmic Reticulum}
    Endoplasmic reticulum (ER) is a network of membranes inside a cell through which proteins and other molecules move. Ribosomes are small and round organelles with the main function to produce the protein needed for the cell. They are located in a continuos membrane system that forms a series of flattened sacs, this membrane is called ER (see Figure \ref{fig:cell}) (\cite{er}). ER itself is moslty located around the nuclei. In order to stain ER were treated with Donkey Anti-Rabbit IgG antibody. This is a fluorescent stain that binds strongly with ER. Its analysis is also important for the CLD as this organelle directly related to the process of protein production within the cell: ER is responsible for the synthesis, folding, modification, and transport of proteins (\cite{er_2}). The proximity of the ER to the nucleus allows essentially controls the protein production. For example, when the protein os misfolded or incorrectly folded it will accumulate in the ER lumen and will serve as a signal to activate misfolded protein response. In contrast to other imaging datasets ER dataset does not require special preprocessing step as the images were of a good quality without any visible problems (see the ground truth image in Figure \ref{fig:er-combined}).
    
    \subsubsection{Training and predictions}
        \input{content/er/convergence.tex}
    \subsubsection{Combination of nuclei and actin predictions}
        \input{content/er/nuclei combined.tex}
    \subsubsection{Postprocessing for ER segmentation}
        \input{content/er/postprocessing.tex}
    \subsubsection{Generalizability across phenotypes}
        TODO move into the other section, there is only 1 phenotype here
        TODO train the model on one phenotype and predict on the other, compare predictions (visually?) 
        postprocessing with metrics then?
        Add metrics
