\subsection{Golgi apparatus}
    The Golgi apparatus (or Golgi, or Golgi complex) is another organelle inside the cell that packages proteins into membrane-bound vesicles which will be exported from the cell. Golgi is also located near the nucleus and ER as well, it is even called a perinuclear body. This location is explained by the biological processes: after a protein comes out of the ER, it goes into the Golgi for further processing (\cite{golgi}). The staining of Golgi apparatus has turned out to be the most difficult of all. Two antibodies were tried out in the beginning, however both of them resulted in a low signal-to-noise ratio. Many images were underexposed, and the density of the cells after their fixation was pretty low. The hypothesis why this was the case was that the choice of target protein in Golgi to which antibody can bind to was not the best. Golgi appartus represents an interest for this study, because it is a very difficult fluorescence target. Even having a fluorescence imaging with high signal-to-noise ratio, the lowest scores among all cell organelles in state-of-the-art paper \cite{Cheng_2021} were achieved on Golgi.
    \subsubsection{Preprocessing}
        \input{content/golgi/golgi preprocessing.tex}
        \paragraph{Background removal algorithms}
            \label{par:background-removal}
            \input{content/background removal.tex}
    \subsubsection{Training and predictions}
        \input{content/golgi/convergence.tex}

    \subsubsection{Alternative ways to improve predictions}
        \paragraph{Asymmetrical losses}
            \input{content/golgi/asymmetrical training.tex}
        \paragraph{Use of gradient in loss}
            One of the insights from the predictions is that there are not enough details inside the predicted fluorescence. The texture and the gradient seem to be missing and predictions are too smooth. Although this is not very crucial for other organelles, Golgi apparatus stain on the other hand has a very granular structure and consists of small dots (see ground truth image in Figure \ref{fig:golgi-no-reg-pcc-predictions}). In order to introduce the granularity we suggest to try the introduction of a gradient of an image into the loss function. For example, by calculating the image gradient with Sobel filters for ground truth and prediction and incorporating the difference into the loss function. Sobel filter is a convolutional operation on the image with two filters, one for detecting horizontal derivative approximations:
            \begin{equation}
                G_x = \begin{bmatrix}
                    1 & 0 & -1\\
                    2 & 0 & -2\\
                    1 & 0 & -1
                    \end{bmatrix} * A, \smallskip
                G_y = \begin{bmatrix}
                    1 & 2 & 1\\
                    0 & 0 & 0\\
                    -1 & -2 & -1
                \end{bmatrix} * A
            \end{equation}
            where A is an image. Then the resulting gradient is:
            \begin{equation}
                G = \sqrt{G_x^2 + G_y^2}
            \end{equation}
        \paragraph{Noise reduction methods}
            \cite{Cheng_2021} put a special attention on the significant importance of a good signal-to-noise ratio for quality Golgi fluorescence predictions. The aforementioned paper uses an advanced denoising algorithm called \textit{noise2void} (\cite{noise2void}). This is a strong method that does not require pairs target clean signal and noisy images available, but simply assumes that that there are only noisy images available. They use the idea that if one could acquire multiple images with the same signal but with different realizations of noise, then after averaging across these images the resulting image would approach the true signal. 

            This might be a useful approach for denoising Golgi imaging instead of the use of enhancement and rolling ball approaches. It is highly advisable to try this method in future research.

    \subsubsection{Conclusions}
        \input{content/golgi/conclusions.tex}