\section{Model robustness and drift detection}
    In this chapter the stability and robustness of the trained models are presented. First subsection shows models' performance on the corrupted DIC input data with two sources of corrupted signal: artificial pseudocorruptions and real corruptions from the microscope settings. It presents the influence of augmentations on the robusteness, studies the influence of corruptions on practical biological metrics and shows how generalizable the models are across phenotypes. Second subsection presents a study of the image representations in the UNet embeddings including their possible clustering in the lower dimensional space based on several possible clustering hypotheses. And finally the last subsection covers the results of the drift detection algorithm built to alert end users when models predictions become unreliable. Which happens when there is a difference between the data used for training and the data used during inference. 
    \input{chapters/stability study/stability.tex}
    \input{chapters/stability study/unet embeddings.tex}
    \input{chapters/stability study/drift detection.tex}
    \subsection{Summary}
    Often appearing during inference DIC image corruptions were analysed with the use of artificial reproducible pseudocorruptions along with the real corruptions acquired from the wrong microscopy settings. Model's predictions degrade with the increasing severity of corruptions, however the use of artificial corruptions in traning mitigates this problem for both real and artificical DIC corruptions. Corruptions influence biological metrics as well, especially total and mean intensities are the two most sensitive metrics. This is directly related to the loss of details in predictions present and therefore it is recommended to pay more attention to intensity metrics during models evaluation. Models are well generalizable from CHOZN to PHX phenotype. Analysis of the lower representation of DIC imaging was carried out through the visualization of UNet embeddings and autoencoder embeddings trained on original DIC data. UNet embeddings reflect the influence of corruptions, however not strongly enough to be used for clustering, whereas autoencoder embeddings do not capture artificial corruptions completely. Two drift detection algorithm were built that are able to successfully differentiate between corrupted and non-corrupted input DIC data based on the UNet embeddings. Both online and offline drift detection algorithms have successfully separated drifted samples from not drifted ones. A usual drift detection algorithm is recommended for a use in the future due to the lower separability between corrupted and not corrupted classes in online version. Tests performed on real microscopic corruptions show that the algorithm is able to detect drift in the real data too, however to evalute the accuracy metrics on these cases more data is needed. Successfull results on the use of drift detector on artificial corruptions shows a great promise for its practical use in order to alert end users when models predictions become unreliable.